### 2010-07-01 trunk/paper/IIWAS2010/content/introduction.tex
updated with clints changes

When traveling though a jungle to a destination, it is easier to get
lost.  The first person to go somewhere may make a number of mistakes
in trying to find the best path to their destination.  However, those
who come later will find it easy to reach that destination if a
well-marked trail has been created. Olsen and Malizia describe this
idea as \emph{exploiting trails} \cite{5379671}.  Rather than treating
a user's discovery experience as a unique entity and working without an example
context, one can exploit the fact that a similar search may have already been
performed.  In one study, almost 40 percent of all queries
were found to be repetitions of previous queries\cite{1277770}. This
indicates the reuse of prior searches is a way to optimize the search
process.  Morpheus is a question answering system motivated by reuse of prior
web search pathways to yield an answer to a user query. Using our analogy,
Morpheus follows path-finders to their destinations and not only marks the
trail, but also provides a taxi service to take followers to similar
destinations.

The Morpheus system employs two distinct roles. One type is called a
\textit{guide} who types queries in the Morpheus web interface and
searches for an answer to the query in an instrumented web browser that can
track answer pathways for a given query. This web tracking tool stores the query
and necessary information to revisit the pathways to the page where the guide 
found the answer. It also provides a mechanism for guides to highlight the answers.
The other role is a \textit{user}, who searches with the Morpheus system much
like a regular search engine, having a natural language interface. The users type a
question in a text box and receive a response from the system. The system
exploits previously answered queries to these answer new questions.

To exploit the prior searches one should represent queries in an elegant way so
that similar queries can be found efficiently and their stored search path
revisited to produce the answer to the user. Morpheus represents user-query details
in a semi structured format called a Semi-Structured Query or \textit{SSQ}. It
includes a user query in natural-language format, relevant terms for the query,
place holders for the term \textit{categories}. A \textit{category} represents a
topic or class to which a term belongs. For example, the term \textit{tire} can be
classified into the category \textit{Automotive Parts}.

Morpheus assumes the term categories are classes of a
\textit{consistent} realm-based ontology. By consistant we mean the ontology has two
properties: (i) singly-rooted heterarchy (acyclic digraph with unique 
ancestor of all nodes) (ii) the subclass/superclass relations have meaningful 
semantic interpretations. This is important because, our proposed similarity 
measure for categories is based on the heterarchically
structured category ontologies. Moreover, when a regular user enters a query,
Morpheus ranks SSQs in the store based on this catgeory similarity. Suppose a
regular user asks -\textit{ a 1997 Toyota Camry V6 needs what size tires?} In
this query, identifying \textit{Camry V6} as a subclass of \textit{Toyota} cars
and a predecessor of \textit{automobile models} is important, because this will
help us grouping stored queries. Similarly, a clean ontology-taxonomy can
improve the recall of such queries by supporting transitivity and other types of
inference like faceted browsing \cite{Wu2008}.

This paper starts by discussing state-of-the-art systems in the area of
question answering and ontology generation. The system
architecture section explains the Morpheus system and its implementations
details. In the results section, we describe current results and its
interpretations. Finally, we conclude the paper by describing the global impacts
of our approaches in QA systems.

>>>>

When traveling though a jungle to a destination, it is easy to get
lost.  The first person to go somewhere may make a number of mistakes
in trying to find the best path to their destination. Those
who come later find it easier to reach the destination if a
well-marked trail has been created. Olsen and Malizia describe this
idea as \emph{exploiting trails} \cite{5379671}.  Rather than treating
a user's discovery experience as a unique entity, one can exploit the fact that a similar search may have already been
performed.  In one study, almost 40 percent of all queries
were repetitions of previous queries\cite{1277770}. Thus, reuse of prior searches is one way to optimize the search
process.  Morpheus is a question answering system motivated by reuse of prior
web search pathways to yield an answer to a user query. Morpheus follows path-finders to their destinations and not only marks the
trail, but also provides a taxi service to take followers to similar
destinations.

There are two distinct Morpheus user roles. A
\textit{path-finder} enters queries in the Morpheus web interface and
searches for an answer to the query using an instrumented web browser. 
This web tracking tool stores the query
and necessary information to revisit the pathways to the page where the path-finder 
found the answer. A \textit{path-follower} uses the Morpheus system much like a regular search engine with a natural language interface. The path-follower enters a question in a text box and receives a guided path to the answer. The system exploits previously found paths to provide an answer.

Morpheus represents user-query details in a semi-structured query (SSQ). It includes a user query in natural-language format, relevant terms for the query, and place holders for the term \textit{categories}. A \textit{category} represents a
topic or class to which a term belongs. For example, the term \textit{tire} can be classified into the category \textit{Automotive Part}.

Morpheus assumes the term categories are classes of a
\textit{consistent} realm-based ontology, that is, one having a singly rooted heterachy whose
subclass/superclass relations have meaningful semantic interpretations. When a path-follower enters a query, Morpheus ranks SSQs in the store based on category similarity. Suppose a
regular user asks -\textit{ a 1997 Toyota Camry V6 needs what size tires?} In
this query, identifying \textit{Camry V6} as a subclass of \textit{Toyota} cars
and a predecessor of \textit{automobile models} is important, because this will
help us grouping stored queries.

This paper discusses related question answering and ontology generation systems in section \ref{sec:relatedwork}. Section \ref{sec:systemarch} explains the Morpheus system and its implementation. Section \ref{sec:results}, we describe current results and their
interpretation. We conclude by describing the global impacts
of our approaches in QA systems.

### 2010-07-01 trunk/paper/IIWAS2010/content/results_discussion.tex
updated with clints changes

As an initial step we created a man-made realm-ontology for the automotive realm
 exploiting the Wikipedia pages, categories, and WordNet synsets. For each of
the categories in the realm-ontolgy we built corpora by grabbing the
corresponding Wikipedia pages. The following section describes question
answering process for a user query, ``A 1997 Toyota Camry V6 needs what size
tires?''

The Morpheus NLP engine parses this query into the constructs: WH:what,
Descriptive Information:1997 Toyota Camry V6, Asking For:size tires. From the
descriptive info, we generate the N-grams or terms 1997, 1997 Toyota, 1997
Toyota Camry,Toyota,Toyota Camry,Toyota Camry V6, Camry, Camry V6, and V6. For
each of the terms, we determined relevant categories (non-increasing order of
relevance) from the ontology corpora. Table \ref{tbl:term_categories} shows
the top categories and their probabilities for each of the query term:

@@

We used this top category of each of the terms in the candidate SSQ and
determined the category divergence with the qualified SSQ categories in the QRM
store. We assumed that all of them belong to the same realm or domain (but, it
is different in real time). In the end, we combined the divergence measure and
ranked QRMs based on the relevance score. Table \ref{tbl:ranked_queries}
shows the top ranked queries that belong to the QRMs in store for the above
query.

@@

\begin{tabular}{| p{3.5cm} | p{3cm} | r |}
\hline
Query & Tagged Categories & Score\\ \hline
A 1997 Toyota Camry V6 needs what size tires? & IC:Sedans, Cars, Engines, Manufactures OC:size tires & 0.91\\ \hline 
What is the tire size for a 1998 Sienna XLE Van? & IC:Vans, Manufactures OC: tire size & 0.72\\ \hline 
Where can I buy an engine for a Toyota Camry V6? & IC:Manufactures, Sedans, Engines OC: where & - \\ \hline 
What is the cost of a Toyota Camry V6 engine? &  IC:Manufactures, Sedans, Engines OC: the clost  & - \\ \hline
\end{tabular}

\caption{Top ranked queries and relevance scores: IC - input categories, OC - output categories}
\label{tbl:ranked_queries}

@@

In this paper, we proposed a novel question answering system that uses previously 
answered user queries to answer similar questions using deep web site.  
The system uses a guide to annotate answer paths so folowing users 
can discover answers to complicated questions.  Each question answer pair is 
assigned a realm, and new questions are matched to the new question answer pairs. 
This query matching strategy assumes that candidate query terms are
available in the category corpus. The candidate query's category annotation will
fail if the query terms are not available. In addition, classification of a
term or n-gram into a category is based on the term frequency distributions in a
classified web document. We are working on improving this
approach by using a probabilistic generative approach as used in the Topic
Models\cite{Blei2003latentdirichlet}.

Similarly, the Morpheus ontology building
process needs categorized web pages. As explained in section
\ref{sec:ontology_generators}, the Wikipedia page categories have some
limitations for this purpose. Without supervision, the page categorization is
often a challenging problem, because topics in the pages that belong to a realm
(e.g. automotive) usually overlap. So we are evaluating the applicability of
probabilistic topic models to web page categorization, and automatic
generation of a realm-ontology based on the topics being extracted.

>>>>

First, we built an ontology for the automotive realm exploiting the Wikipedia pages, categories, and WordNet synsets. For each of the classes in the ontolgy we built corpora from the corresponding Wikipedia pages. Figure \ref{fig:automotive_ontology} shows a subsection of this ontology.

 describes the question answering process for the user query, ``A 1997 Toyota Camry V6 needs what size tires?''

%% TODO - need to refer back to the table which is figure one.
%The Morpheus NLP engine parses this query into the constructs: WH:what, Descriptive Information:1997 Toyota Camry V6, Asking For:size tires. From the descriptive info, we generate the N-grams or terms 1997, 1997 Toyota, 1997 Toyota Camry,Toyota,Toyota Camry,Toyota Camry V6, Camry, Camry V6, and V6. For each of the terms, we determined relevant categories (non-increasing order of relevance) from the ontology corpora. Table \ref{tbl:term_categories} shows the top categories and their probabilities for each of the query term.
In Table \ref{tbl:nlp_engine_parse} we show the data that is output by the Morpheus NLP engines parse of the query .  It extracts the WH question

\begin{table}[h]\footnotesize
	\begin{tabular}{|l|p{4.2cm}|}
		\hline 
		WH & what \\
		\hline 
		Descriptive Information & 1997 Toyota Camry V6 \\
		\hline 
		Asking for & size tires \\
		\hline 
		ngrams & 1997, 1997 Toyota, 1997 Toyota Camry, Toyota, Toyota Camry, Toyota Camry V6, Camry, Camry V6, V6 \\
		\hline
	\end{tabular}
	\caption{The output of NLP engine parse}
	\label{tbl:nlp_engine_parse} 
\end{table}

@@

We found the top category of the terms in the candidate SSQ and determined the category divergence with the qualified SSQ classes in the QRM store. Then, we combined the divergence measure and
ranked QRMs based on the relevance score. Table \ref{tbl:ranked_queries} shows the top ranked SSQ for the query.  Finally, we execute the selected QRM and display the results to the user.

@@

\begin{tabular}{| p{3.5cm} | p{3cm} | r |}
\hline
Query & Tagged Classes & Score\\ \hline
A 1997 Toyota Camry V6 needs what size tires? & IC:Sedans, Cars, Engines, Manufactures OC:size tires & 0.91\\ \hline 
What is the tire size for a 1998 Sienna XLE Van? & IC:Vans, Manufactures OC: tire size & 0.72\\ \hline 
%Where can I buy a headlight for a Toyota Camry V6? & IC:Manufactures, Sedans, Engines OC: where & - \\ \hline 
%What is the cost of a Toyota Camry V6 muffler? &  IC:Manufactures, Sedans, Engines OC: the clost  & 0.97 \\ \hline
\end{tabular}

\caption{Top ranked queries and relevance scores: IC - input classes, OC - output classes}
\label{tbl:ranked_queries}

@@

In this paper, we propose a novel question answering system that uses the deep web and previously answered user queries to answer similar questions. The system uses a path-finder to annotate answer paths so path-followers can discover answers to similar questions.  Each $(question, answer)$ pair is assigned a realm, and new questions are matched to the new $(question, answer)$ pairs. Classification of terms into classes is based on term frequency distributions in our corpora of web documents. We are investigating improvements to our solution by an approach similar to Topic Models \cite{Blei2003latentdirichlet}.

Manually forming a corpus of wilipedia pages associated with a class is a cumbersome task. Topic Modeling provides a promising approach to identifying pages relevent to given class in a more automated manner.
%The Wikipedia page categories has limitations. Without supervision, the page categorization is often a challenging problem, because topics in the pages that belong to a realm (e.g. automotive) usually overlap. So we are evaluating the applicability of probabilistic topic models to web page categorization, and automatic generation of a realm-ontology based on the topics being extracted.
